Canadian Household Internet Productivity and Recreation Trends 2018

### 2022-04-28 outputs/paper/paper.Rmd
finalize paper

---
title: "Impact of Internet Infrastructure on Canadian Household Productivity and Recreation"
subtitle: "Brief Overview of Canadian Internet Use Trends"
author: "Haocong Wu"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "Code and data are available at: https://github.com/hcgw0318/2018-Canadian-Internet-Use-Analysis"
abstract: "Internet access is critical to many users. This paper examines the quality of internet access that users have and how they are impacted by subpar service. With data collected by Statistics Canada in the Canadian Internet Use Survey, and modelled with linear regression, age has a negative correlation with user household internet usage, whilst education level has a strong positive correlation."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

This paper examines the causal relations between individual internet usage amounts to factors such as connection speed,nature of use, and necessity of use.

@@

@@

```{r internethours, fig.cap="Respondent weekly internet use", echo=FALSE}
ggplot(cius_data, aes(x=hours_used))+
  geom_bar(stat = "count") + 
  theme(axis.text.x = element_text(angle = -15, vjust = 1, hjust=0)) + 
  labs(x = "Duration of use",
       y = "Count",
       title = "Hours of internet use per week (excluding entertainment)")
```

@@

```{r regressionmodel, fig.cap="2018 Canadian Internet Use Regression Model", echo=FALSE}
modelsummary(lm_model, fmt=1, title = "Model of weekly internet use quantity")
```

@@

@@

@@

@@

>>>>

---
title: "Canadian Household Internet Productivity and Recreation Trends 2018"
subtitle: "Brief Overview of Canadian Internet Use Trends"
author: "Haocong Wu"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "Code and data are available at: https://github.com/hcgw0318/2018-Canadian-Internet-Use-Analysis"
abstract: "Internet access is critical to many users. This paper examines the quality of internet access that users have and how they are impacted by subpar service. With data collected by Statistics Canada in the Canadian Internet Use Survey, and modelled with linear regression, age has a negative correlation with user household internet usage, whilst education level has a strong positive correlation."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

This paper examines the causal relations between individual internet usage amounts to factors such as connection speed, nature of use, and necessity of use.

@@

\newpage

@@

```{r internethours, fig.cap="Respondent weekly internet use", echo=FALSE}
ggplot(cius_data, aes(x=hours_used))+
  geom_bar(stat = "count") + 
  theme(axis.text.x = element_text(angle = -15, vjust = 1, hjust=0)) + 
  labs(x = "Duration of use",
       y = "Count",
       title = "Hours of internet use per week")
```

@@

```{r regressionmodel, fig.cap="2018 Canadian Internet Use Regression Model", echo=FALSE}
modelsummary(lm_model, fmt=1, title = "Model of weekly internet use quantity") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), latex_options = "HOLD_position") %>%
  kable_paper("striped", full_width = F)
```

@@

From data displayed in Table \@ref(tab:demotab1) and graphed, the respondent demographic can be seen to have a larger female representation. This observation could be caused by a larger proportion of Canadian females being available to pick up the phone due to childcare and household work.

@@

Despite the decreasing proportion of individuals at each age group that uses the internet shown in Figure \@ref(fig:agegroup), the number of respondents increases with each older age group. This at first glance seems conflicting with the fact that the CIUS is  conducted primarily on an online platform. A reason for this occurrence may be that the older age groups have more leisure time, and are willing to use their leisure time to respond to this survey.

@@

As education level increases, the proportion of respondents that use the internet increases, as shown in Figure \@ref(fig:educationlevel). In addition, the amount of time that one uses the internet per week increases with education level as well. This result likely arises due to the utility if not necessity of utilizing online resources to progress with further education, as well as the fact that individuals who undertake further education would be more inclined to adapt and utilize new technology.

The converse is true with age, the younger the respondent, the more likely they are to both use the internet and use it for a longer duration per week, this is depicted by Figure \@ref(fig:agegroup). This occurrence is explainable by the attraction of online entertainment of social media, video games, and media consumption platforms to younger audiences. The younger the individual, the more accustomed they are to seek entertainment through online means.

@@

This paper attempts to address the current populations internet usage tendencies, and focuses on the duration of internet use. The respondents' demographics, connection type, and usage purposes were variables that were analyzed. Given that the goal of the paper is to find correlation between these factors and internet usage hours, the analysis that consisted of the factors of gender, age, education, and usage nature may be lacking. The analysis can be supplemented with the consideration of factors such as household economy, urban and rural living distinctions, and whether anyone in their household utilized the internet. These factors were not included in the survey, and can be collected from a follow-up supplemental survey.

Another weakness of the analysis is making the assumption of generating uniform random ages for each age group to perform linear regression. This assumption was made due to the lack of more granular internet usage data. To improve on this aspect, perhaps ordinal regression may be a better fit to generate a model.

\newpage
